---
title: ""
author: ""
date: "`r Sys.Date()`"
format: html
params:
  extra_path: ""
---

# Set-up 

```{r setup, cache = FALSE}
require(knitr)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
table = function (..., useNA = 'ifany') base::table(..., useNA = useNA)

# Use extra path for R packages already installed
if (length(params$extra_path) != 0){
  .libPaths(c(params$extra_path,.libPaths()))
}
```

```{r message = FALSE, warning=FALSE}
# libraries for data analysis
library(dplyr)
library(tidyr)
library(tibble)
library(lubridate)
library(magrittr)
library(janitor)
library(purrr)
library(stringr)

# For data viz
library(ggplot2)
library(patchwork)

# libraries for knitting qmd
library(downlit)
library(formatR)

# confirm working directory
getwd()
```
## R and Rmarkdown Style Guide 

1) Blank slate 

Always restart your Rstudio session at least once per day to ensure that your code is not missing any variables or code chunks. 

https://rstats.wtf/source-and-blank-slates#always-start-r-with-a-blank-slate 

https://rstats.wtf/source-and-blank-slates#restart-r-often-during-development 

2) Save Large and Important Objects 

 
Always save Save Large and Important Objects, as well as intermediate results if it takes a long time to generate. 

Be sure to name it appropriately or add a README or note in your Rmd/qmd about that specific object. 

https://rstats.wtf/source-and-blank-slates#objects-that-take-a-long-time-to-create 


3) RStudio R Projects 

Use Rprojects for all data analyses with Rmarkdown and quarto.

https://rstats.wtf/projects#rstudio-projects 


4) File Naming 

Ensure all filenames as outputs follow these guidelines.

https://speakerdeck.com/jennybc/how-to-name-files 

  

# Background

please see attached list of the samples we sequenced with the following info:
  - [...]


### Collaborators

- [NAME 1]
- [NAME 2]
- [...]

- Department of Pediatric Hematology-Oncology, and Cell and Gene Therapies

- Bambino Gesù Children's Hospital

# Define Data and File Locations

```{r}
#| eval: true
#| 
# processed with rnaseq_count_nf/ pipeline 
# data outputs saved in lab shared storage
INPUT <- file.path("/mnt/network_drives/storage-bioinfo_labq")

if(!dir.exists("data/")){
  dir.create("data/", recursive = TRUE)
  link_command <- system(glue::glue("ln -f -s {INPUT} data/"))
}
```

```{r}
# point to symlinked directory that contains the results of a workflow
DATA <- file.path("data/")
dir(DATA)
```

```{r}
# create an informative prefix for all files that are generated in the analysis notebook here. 
# Checkout the ## R and Rmarkdown Style Guide section above for more details. 
PREFIX <- "2025.00.00_XXXX"
```

```{r}
# filepath for sample metadata and sequencing run logs 
metadata_path <- glue:::glue("{DATA}/metadata")
```


# Clinical Data


# Sample Metadata

```{r}
# initial metadata files
metadata <- file.path(metadata_path, glue::glue("{PREFIX}")) %>%
  janitor::clean_names()

# cleaned metadatafiles
meta_out <- file.path(metadata_path,glue::glue("{PREFIX}_sample_annots.tsv"))
```

# Quality Control 


# Unsupervised Clustering


# Perform Differential Expression


# QC Plots 


# Session Information

```{r}
sessionInfo()
```
