---
title: ""
author: ""
date: "`r Sys.Date()`"
format: html
---

# Set-up 

```{r setup, cache = FALSE}
require(knitr)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),
                      tidy=TRUE,
                      fig.align='center',
                      fig.width = 10, fig.height = 10)

options(stringsAsFactors = FALSE)
table = function (..., useNA = 'ifany') base::table(..., useNA = useNA)
```

```{r message = FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)

getwd()
```

# Background

please see attached list of the samples we sequenced with the following info:
  - [...]


### Collaborators

- [NAME 1]
- [NAME 2]
- [...]

- Department of Pediatric Hematology-Oncology, and Cell and Gene Therapies

- Bambino Gesù Children's Hospital

# Clinical Data


# Sample Metadata


# Quality Control 


# Unsupervised Clustering


# Perform Differential Expression


# QC Plots 


# Session Information

```{r}
sessionInfo()
```